---
title: "Your Social Network Report"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
date: 'DATE-HERE'
params:
  qualtricsLink: "https://INSERT_QUALTRICS_LINK_HERE"
  datafile: '/socialnetworktest3.csv' #INPUT YOUR FILE NAME HERE
  PID: 10 ## INPUT PARTICIPANT ID HERE
---

```{r setup functions, include=FALSE, echo=FALSE}

PID = params$PID 
qualtricsLink = params$qualtricsLink

#### PACKAGES #####
library(igraph); library(tidyverse); library(flextable)

###### DATA READING ######
  #before importing datafile, remember to delete rows 2 - 3 on the .csv file. They are extra headers. When you import the data, you should only have one header row. 
socialNet = read.csv(params$datafile) 

### DATA CLEANING ####
socialNet = socialNet %>% select(27:ncol(socialNet)) # get rid of the unnecessary first 26 columns
colnames(socialNet)[2:21] = sub("_1", "", colnames(socialNet)[2:21]) #fix column names for columns 2 - 21 to get rid of "_1" 
colnames(socialNet) #column names
      #columns 2:31 and 42:51 are network nodes; columns 52:96 are network edges 

### DEFINE FUNCTIONS TO CREATE INDIVIDUAL PARTICIPANT'S SOCIAL NETWORK ####
makeSocialNetworkNodes <- function(dataframe, ParticipantID) { #function to create dataframe for participant's social network nodes
  nodes = reshape(dataframe[which(dataframe$PID ==ParticipantID), c(2:51)], 
                  varying = list(c(paste0(rep("p", each=10),rep(1:10,1))),
                                 c(paste0(rep("p", each = 10),rep(1:10, 1), rep("_age", each=10))),
                                 c(paste0(rep("p", each = 10),rep(1:10, 1), rep("_gender", each=10))),
                                 c(paste0(rep("p", each = 10),rep(1:10, 1), rep("_race", each=10))),
                                 c(paste0(rep("close_p", each = 10),rep(1:10, 1)))),
                  direction = 'long',
                  timevar = "person",
                  times = paste0(rep("Person", each=10),rep(1:10,1)),
                  v.names = c('name','age','gender','race','close')) %>% 
    filter(!is.na(name)) %>% 
    select(-id) %>% 
    mutate(gender = factor(gender, levels=c(1,2,3), labels=c('Male','Female','Other')),
           race = factor(race, levels=c(1,2,3,4,5,6), labels=c('White','Black','Amer. Indian or Alaska Native','Asian','Latino/a','Other')),
           age_group = factor(case_when(age < 18 ~ 'Below 18',
                                 age > 17 & age <25 ~ '18-24',
                                 age > 24 & age <35 ~ '25-34',
                                 age > 34 & age <45 ~ '35-44',
                                 age > 44 & age <55 ~ '45-54',
                                 age > 54 & age <65 ~ '55-64',
                                 age > 64 ~ '65+'),
                              levels=c('Below 18', '18-24','25-34','35-44','45-54','55-64')))
  
  return(nodes)
}

makeSocialNetworkEdges <- function(dataframe, ParticipantID){ #function to create dataframe for participant's social network edges
  edges = data.frame("from" = colnames(dataframe[which(dataframe$PID ==ParticipantID),c(52:96)] %>% 
                                 select(where(function(x) !is.na(x)& x > 0)))) %>% 
                                  separate("from", c("from","to"))
  return(edges)
}
```

About 6 weeks ago, you completed a survey that included questions about your current social networks. Specifically, you were asked to list up to 10 different individuals from the past one year with whom you like to spend your free time for informal social activities such as going out to lunch, dinner, drinks, films, visiting one another's homes, and so on.

Please review your "Current Social Network Report" below.

```{r participant social network results, echo=FALSE}
#nodes and edges
networkNodes = makeSocialNetworkNodes(socialNet, PID) 
networkEdges = makeSocialNetworkEdges(socialNet, PID)

#gender
genderFreq = data.frame(table(networkNodes$gender)) %>% 
  filter(Freq>0) %>% 
  mutate(percent = paste(Freq/sum(Freq)*100, '%', sep = "")); colnames(genderFreq) = c('Gender','count','percent')

#race
raceFreq = data.frame(table(networkNodes$race)) %>% filter(Freq>0) %>% mutate(percent = paste(Freq/sum(Freq)*100,'%', sep = "")); colnames(raceFreq) = c('Race','count','percent')

#age groups
ageFreq = data.frame(table(networkNodes$age_group)) %>% filter(Freq>0) %>% mutate(percent = paste(Freq/sum(Freq)*100, '%', sep = "")); colnames(ageFreq) = c('age_group','count','percent')

```

## Your current social network

Based on the information you gave us, the composition of your social network is:

::: {style="display: flex;"}
<div>

#### Gender

```{r genderPlot, echo=FALSE, fig.height = 3, fig.width = 3, fig.align = "center"}
ggplot(genderFreq, aes(x='', fill=Gender, y=count))+
  geom_bar(width = 1, stat='identity', color='black')+
  coord_polar("y") +
  theme_void()+
  labs(fill='')+
  scale_fill_manual(values=c('#a6cee3','#b2df8a','#1f78b4'))+
  geom_text(aes(label = percent),
            position = position_stack(vjust = 0.5), size=3)
```

</div>

<div>

#### Race

```{r racePlot, echo=FALSE, fig.height = 3, fig.width = 3, fig.align = "center"}

ggplot(raceFreq, aes(x='', fill=Race, y=count))+
  geom_bar(width = 1, stat='identity', color='black')+
  coord_polar("y") +
  theme_void()+
  labs(fill='')+
  scale_fill_brewer(palette='RdYlGn')+
  geom_text(aes(label = percent),
            position = position_stack(vjust = 0.5), size=3)
```

</div>

<div>

#### Age groups

```{r agePlot, echo=FALSE, fig.height = 3, fig.width = 3, fig.align = "center"}
ggplot(ageFreq, aes(x='', fill=age_group, y=count))+
  geom_bar(width = 1, stat='identity', color='black')+
  coord_polar("y") +
  theme_void()+
  labs(fill='')+
  scale_fill_brewer(palette='RdPu')+
  geom_text(aes(label = percent),
            position = position_stack(vjust = 0.5), size=3)
```

</div>
:::

## Social Network

Below is a visualization of your existing social network. This plot visualizes who is tied to whom; if there is a line connecting two circles, that means those two individuals know each other. The network nodes are colored based on gender: the light blue nodes are men, the green nodes are women, and the dark blue nodes indicate a gender identity other than male or female. The size of the nodes represent how close the person is to you.

```{r socialNetworkPlot, echo=FALSE,fig.align = "center"}
### SOCIAL NETWORK PLOT ###
socialNetPlot <- graph_from_data_frame(d=networkEdges, vertices=networkNodes, directed=F)  #create igraph object
V(socialNetPlot)$color = ifelse(V(socialNetPlot)$gender =="Male",'#a6cee3', #males = light blue
                                ifelse(V(socialNetPlot)$gender =="Female",'#b2df8a', '#1f78b4')) #females = green, other = dark blue
V(socialNetPlot)$size <- V(socialNetPlot)$close*12 #set node sizes based on participant's rating of closeness to self

par(mar=c(0,0,0,0)+.1)
plot(socialNetPlot, vertex.label.color="black", vertex.label = V(socialNetPlot)$name)
```

##### Our analyses of your social network has extracted the following information:

##### Closeness

Closeness for each individual can be found in the table below.

Closeness refers to how easily the focal individual can reach or be reached. An individual with higher closeness number means that individual can be easily reached; in other words, they will get first whatever is circulating (e.g., news, gossip) which can be good or bad depending on what the content of circulation is.

```{r closenessTable, echo=FALSE, warning=FALSE}

closeness(socialNetPlot, mode="all", weights=NA) %>% 
  data.frame() %>% 
  rownames_to_column('name') %>% 
  setNames(., c('Name','Closeness')) %>% 
  regulartable() %>% autofit() %>% 
width(j=~Name,width=1) %>% width(j=~Closeness,width=1)

```

##### Cliques

A clique refers to a group of individuals where everybody is connected directly to everyone else. A social network can consist of just 1 central clique, where everyone within the network is connected, or multiple cliques within a network. Analysis of your network is visualized below.

```{r cliques, echo=FALSE, warning=FALSE,fig.align = "center"}
par(mar=c(0,0,0,0)+.1)
plot(cluster_edge_betweenness(socialNetPlot), socialNetPlot)

```

##### Density

Network density refers to the portion of the potential connections in a network that are actually connections. This number is out of one. The higher the ratio, the more interconnected your network is. Your network density is:

```{r density, echo=FALSE}
cat(edge_density(socialNetPlot, loops = FALSE))
```

------------------------------------------------------------------------

### Final study phase

When you have reviewed your social network analysis, follow the link below to complete the final phase of the study. The final survey should take about 15 - 30 minutes.

*Wait until you have enough time in a quiet spot to finish the survey in one sitting without distractions.*

<br><Br>

::: {style="text-align:center"}
<button>
```{r results='asis', echo = FALSE}
cat("[LINK TO FINAL PHASE OF STUDY](", qualtricsLink,"?PID=",PID, ")", sep='')
```
</button>
:::

## <Br><Br>
